Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation--extrapolation capacity validation

### 2022-10-14 Article.tex
Initial clean of the TeX file

%\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
%\newcommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
%\newcommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
%\newcommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
%\newcommand{\ERMS}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$ ) and temperatures ($1050^\circ\text{C} -1250^\circ$C ). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $AARE$ and the Root Mean Square Error ($RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.  
\end{abstract}

@@

%----------------------------------------------
\section{ Materials and Experiments \label{sec:Materials}}
%----------------------------------------------
%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------
The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}. Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm. Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$. Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests. The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients. Then cooled to test temperature where the specimen is held $1$ minute before deformation. After compression the specimen is quencted rapidly for microstructure studies. The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/Gleeble-3}
\caption{Gleeble 3800 simulator system}
\label{fig:Gleeble3800}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/GleebleDesign}
\caption{Schematic diagram of the experimental process.}
\label{fig:Heating}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
\scalebox{0.9}{
\begin{tabular}{lcccccccc}
\hline
C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
\hline
 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
\hline
\label{tab:Composition}
\end{tabular}}
\end{table}
%------------------------------------------------------------------------
\subsection{Flow stress behavior}
%------------------------------------------------------------------------
The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}. From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature. It should be noted that the strain influences the flow stress. Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test. The peak stress value increases with strain rate but decreases with temperature. For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test. The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test. For low strain rates, lubrication is lost over time and therefore friction occurs. This results in a progressive increase in stress.

To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening. As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC. During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains. The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress. DRX consists of the germination of new grains, at the borders or inside the initial grains. These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy. As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression. As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate. Indeed, most of the grain boundaries start to form new grains. The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/BeforeCompM}
\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
\label{fig:BeforeCompM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{newFigures/AfterCompM}
\caption{Optical micrograph of AISI P20 alloy after howt compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
\label{fig:AfterCompM}
\end{figure}

@@

{newFigures/JCSigmaAB}

@@

{newFigures/JCSigmaAB1}

@@

{newFigures/JCSigmaT}

@@

The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates. All parameters of JC model are in Table \ref{tab: JCparameters}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model} 
\label{fig:iCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\scalebox{1.2}{
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
\hline
\label{tab: JCparameters}
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
\scalebox{0.83}{
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

{newFigures/CompExpHS}

@@

\includegraphics[width=0.9\columnwidth]{newFigures/LnAlp}

@@

\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE0}

@@

\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhE}

@@

\includegraphics[width=0.9\columnwidth]{newFigures/LnSinhT}

@@

\includegraphics[width=1.02\columnwidth]{newFigures/ARparameters}

@@

{newFigures/CompExpAR}

@@

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}. The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good. The deviation between the predicted values and the experimental values is relatively good.
\begin{table}[!h]
\centering{}
\caption{Parameters of PTM model\label{tab:PTM-parameters}}
\scalebox{0.83}{
\begin{tabular}{cc}
\hline
&   \\
Parameters &Values\\
&   \\
\hline
$A_0 (\text{MPa})$ & $62.314$ \\
$A_1 (\text{MPa})$ & $559.827$ \\
$A_2 (\text{MPa})$ & $-2160.03$ \\
$A_3 (\text{MPa})$ & $4641.94,$ \\
$A_4 (\text{MPa})$ & $-5193.06$ \\
$A_5 (\text{MPa})$ & $2379.1$ \\
$B_0 $   & $-0.0035805$\\
$B_1 $   & $0.00282334$ \\
$B_2 $   & $-0.00775301$\\
$B_3 $   & $0.0085135$ \\
$B_4 $   & $-0.00412815$\\
$C_0^0 $ & $0.148304$ \\
$C_0^1 $ & $-0.301958$ \\
$C_0^2 $ & $2.2706$ \\
$C_0^3 $ & $-5.33003$ \\
$C_0^4 $ & $5.48971$ \\
$C_0^5 $ & $-2.11566$\\
$C_1^0 $ & $-3.74842\ \times10^{-7}$\\
$C_1^1 $ & $0.00165233$\\
$C_1^2 $ & $-0.00270485$ \\
$C_1^3 $ & $-0.000483867$\\
$C_1^4 $ & $0.00174818$ \\
\hline
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{newFigures/CompExpPTM}
\caption{Comparison between the experimental and predicted flow stresses by PTM model }
\label{fig:iCorrelationPTM}
\end{figure}
\FloatBarrier

>>>>

\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
\newcommand{\RMSE}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050^\circ\text{C} -1250^\circ$C). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot{\varepsilon}^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050^\circ$C and $1100^\circ$C  while in the case of the PTM model, the strain rate  ($\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot{\varepsilon}^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
\end{abstract}

@@

%----------------------------------------------
\section{ Materials and Experiments \label{sec:Materials}}
%----------------------------------------------
%----------------------------------------------
\subsection{Experimental procedure}
%----------------------------------------------
The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in the Table \ref{tab:Composition}. Cylindrical specimens were machined with an initial diameter of $10$ mm and a height of $15$ mm. Hot compression tests were conducted on a Gleeble-3800 thermo-simulator (Figure \ref{fig:Gleeble3800}), at temperatures of $1050^\circ$C,  $1050^\circ$C,  $1100^\circ$C,  $1150^\circ$C,  $1200^\circ$C and  $1250^\circ$C with strain rates of $0.001\ \text{s}^{-1}$, $0.01\ \text{s}^{-1}$, $0.1\ \text{s}^{-1}$, $1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$. Thin tantalum sheets were used as a lubricant material at the contact surface of anvils and specimen to minimize the frictions during the tests. The samples were heated up to temperature $1260^\circ$C  and were held for $5$ min to eliminate thermal gradients. Then cooled to test temperature where the specimen is held $1$ minute before deformation. After compression the specimen is quencted rapidly for microstructure studies. The procedure of this test is illustrated in Figure \ref{fig:Heating} where $h_0$ and $R_0$ are the height and radius before compression; $h$, $R_M$, and $R_T$ are respectively the height, big radius and small radius of the specimen after compression.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/Gleeble-3800}
\caption{Gleeble 3800 simulator system}
\label{fig:Gleeble3800}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/GleebleDesign}
\caption{Schematic diagram of the experimental process.}
\label{fig:Heating}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Chemical Composition of the AISI P20 Steel (Weight Percent)}
\scalebox{0.9}{
\begin{tabular}{lcccccccc}
\hline
C  &Mn & Mo   & Si   & Ni       &Cr& Cu & Other& Balance\\
\hline
 0.30        &       0.89      &0.52		   &	0.34     &	 0.68          &1.86& 0.17& Microalloying& Iron\\
\hline
\label{tab:Composition}
\end{tabular}}
\end{table}
%------------------------------------------------------------------------
\subsection{Flow stress behavior}
%------------------------------------------------------------------------
The flow stress curves obtained from the compression tests performed on Gleeble-3800 simulator for each test condition are shown in Figure \ref{fig:rawData}. From these curves it can be seen that the flow stress increases with increasing strain rate but decreases with increasing temperature. It should be noted that the strain influences the flow stress. Indeed, for all strain values below $0.2$, the stress increases with strain before reaching a peak value at low strain rates and then decreases to maintain a stable value until the end of the test. The peak stress value increases with strain rate but decreases with temperature. For higher strain rates ($1.0\ \text{s}^{-1}$, $2.0\ \text{s}^{-1}$ and $5.0\ \text{s}^{-1}$) the flow stress increases throughout the test. The slight increase in stress at low strain rates when the strain is large is due to friction between the specimen and the grip during the test. For low strain rates, lubrication is lost over time and therefore friction occurs. This results in a progressive increase in stress.

To explain the overall behavior of the flow stresses observed during this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX). At the beginning of the deformation, the amount of dislocations increases and they start to move, leading to a rapid increase in stress known as work-hardening. As the strain continues to increase, the dislocations are set in motion, leading to a stress relaxation phenomenon usually known as DRC. During this DRC mechanism, some of the dislocations are removed, due to their combination with another dislocation, or due to their integration into a grain boundary, and some of them are rearranged and formed as sub-grains within the initial grains. The combination of these dislocations moderates the increase of dislocations linked to strain hardening and thus controls the amount of energy stored in the material and manages the increase in flow stress. DRX consists of the germination of new grains, at the borders or inside the initial grains. These two phenomena therefore explain the different shapes of the flow stress curves observed for this alloy. As an example, the Figure \ref{fig:BeforeCompM} and Figure \ref{fig:AfterCompM} show the microstrutures of AISI P20 before and after compression. As observed on the flow curves, it can be seen that recrystallisation is almost complete for this temperature and strain rate. Indeed, most of the grain boundaries start to form new grains. The identification of the behavioral laws of these curves will be done in the next section in order to predict its behavior in any test condition.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/BeforeCompM}
\caption{Optical micrograph of the AISI P20 steel before hot compression held during $5$ minutes at $1260^\circ$C}
\label{fig:BeforeCompM}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]
{Figures/AfterCompM}
\caption{Optical micrograph of AISI P20 alloy after hot compression with a strain rate $0.001\ \text{s}^{-1}$ under $1150^\circ$C.}
\label{fig:AfterCompM}
\end{figure}

@@

{Figures/JCSigmaAB}

@@

{Figures/JCSigmaAB1}

@@

{Figures/JCSigmaT}

@@

The predicted and experimental values are compared, as shown in Figure \ref{fig:iCorrelationJC}. The JC model is not much suitable to describe the ﬂow behavior of AISI P20 within entire deformation condition, and predicted values show a monotonous downward trend at various strain rates. The deviation between predicted values and experimental values is large for the low strain rates and almost acceptable at high strain rates. All parameters of JC model are in Table \ref{tab: JCparameters}.
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model}
\label{fig:iCorrelationJC}
\end{figure}
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Johnson-Cook Model}
\scalebox{1.2}{
\begin{tabular}{lccccc}
\hline
&         &             &		   &		  &\\
Parameters&$A(\text{MPa})$    &$B(\text{MPa})$        & $n$     & $C$   & $m$       \\
&         &             &		   &	     &	    \\
\hline
Values&$43.0988$&$114.518$& $0.313969$&$0.0995438$&$0.898932$\\
\hline
\label{tab: JCparameters}
\end{tabular}}
\end{table}
%-------------------------------------------------------------------------
\subsection{Modified Zerilli--Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot{\varepsilon}^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot{\varepsilon}^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot{\varepsilon}^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot{\varepsilon}^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{tize2022generalized}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified--Zerilli-Armstrong Model}
\scalebox{0.83}{
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

{Figures/CompExpHS}

@@

\includegraphics[width=0.9\columnwidth]{Figures/LnAlp}

@@

\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE0}

@@

\includegraphics[width=0.9\columnwidth]{Figures/LnSinhE}

@@

\includegraphics[width=0.9\columnwidth]{Figures/LnSinhT}

@@

\includegraphics[width=1.02\columnwidth]{Figures/ARparameters}

@@

{Figures/CompExpAR}

@@

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}. The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the strain rate $\mdot{\varepsilon}^p = 0.1\ \text{s}^{-1}$ the prediction in not quite good. The deviation between the predicted values and the experimental values is relatively good.
\begin{table}[!h]
\centering{}
\caption{Parameters of PTM model\label{tab:PTM-parameters}}
\scalebox{0.83}{
\begin{tabular}{cc}
\hline
&   \\
Parameters &Values\\
&   \\
\hline
$A_0 (\text{MPa})$ & $62.314$ \\
$A_1 (\text{MPa})$ & $559.827$ \\
$A_2 (\text{MPa})$ & $-2160.03$ \\
$A_3 (\text{MPa})$ & $4641.94,$ \\
$A_4 (\text{MPa})$ & $-5193.06$ \\
$A_5 (\text{MPa})$ & $2379.1$ \\
$B_0 $   & $-0.0035805$\\
$B_1 $   & $0.00282334$ \\
$B_2 $   & $-0.00775301$\\
$B_3 $   & $0.0085135$ \\
$B_4 $   & $-0.00412815$\\
$C_0^0 $ & $0.148304$ \\
$C_0^1 $ & $-0.301958$ \\
$C_0^2 $ & $2.2706$ \\
$C_0^3 $ & $-5.33003$ \\
$C_0^4 $ & $5.48971$ \\
$C_0^5 $ & $-2.11566$\\
$C_1^0 $ & $-3.74842\ \times10^{-7}$\\
$C_1^1 $ & $0.00165233$\\
$C_1^2 $ & $-0.00270485$ \\
$C_1^3 $ & $-0.000483867$\\
$C_1^4 $ & $0.00174818$ \\
\hline
\end{tabular}}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpPTM}
\caption{Comparison between the experimental and predicted flow stresses by PTM model }
\label{fig:iCorrelationPTM}
\end{figure}
\FloatBarrier

%-------------------------------------------------------------------------
\subsection{Artificial neural network model\label{sec:ANNmodel}}
%--------------------------------------------------------------------------
The Artificial Neural Network model (ANN) is a mathematical formulation widely used in many fields today for better prediction. It is a model based on the principle of minimisation where it improves from the progressive decrease of the error during the learning process. Typically an ANN model contains an input layer, an output layer and hidden layers. Each hidden layer is connected to the one before it and the one after it via neurons. Indeed, all neurons in the $k$ layer are connected to each neuron in the ($k+1$) layer. To each layer is added another parameter called bias. As said the principle of the ANN model is therefore based on the minimisation of the difference between the value obtained from the output of the network and the expected value.  Indeed, once the error is calculated, it is propagated back to the input layer in order to update the model parameters via the minimisation algorithms. In our case, the ADAM algorithm is used. The architecture of the network used in this study is shown in Figure \ref{fig:ANN-scheme-2HL}. After several tests of different types of network architecture, it was found that two hidden layers including $15$ neurons for the first hidden layer and $7$ for the second one gives the best prediction where the input layer is composed of three neurons ($\varepsilon^p$, $\mdot{\varepsilon}^p$, $T$) and the output layer is composed of a single neuron corresponding to the flow stress. The good performance of the model is found to be stable between $800$ and $1000$ epochs.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture \cite{OPantale-2021-LGP}.}
\label{fig:ANN-scheme-2HL}
\end{figure}
